\documentclass[10pt,sigconf]{acmart}
\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
\pagestyle{plain}
\setcopyright{none}

\usepackage[utf8]{inputenc}
\usepackage{booktabs}
\usepackage{array}
\usepackage{hyperref}
\usepackage{commath}
\newcommand*\rotbf[1]{\rotatebox{90}{\textbf{#1}}}
\newcommand{\specialcell}[2][c]{\begin{tabular}[#1]{@{}l@{}}#2\end{tabular}}
\newcommand{\specialcellbold}[2][c]{
  \bfseries
  \begin{tabular}[#1]{@{}l@{}}#2\end{tabular}
}

\begin{document}
\title{Comment Volume Prediction}
\subtitle{Text Mining in Practice} 

\author{Johannes M. Kroschewski}
\affiliation{
	\institution{Hasso-Plattner-Institut,\\ University of Potsdam}
	\streetaddress{Prof.-Dr.-Helmert-Str. 2–3}
	\city{Potsdam} 
	\state{Germany} 
	\postcode{14482}
}
\email{johannes.kroschewski@student.hpi.de}

\author{Friedrich C. Schöne}
\affiliation{
	\institution{Hasso-Plattner-Institut,\\ University of Potsdam}
	\streetaddress{Prof.-Dr.-Helmert-Str. 2–3}
	\city{Potsdam} 
	\state{Germany} 
	\postcode{14482}
}
\email{friedrich.schoene@student.hpi.de}

\author{Nils H. Straßenburg}
\affiliation{
  	\institution{Hasso-Plattner-Institut,\\ University of Potsdam}
	\streetaddress{Prof.-Dr.-Helmert-Str. 2–3}
	\city{Potsdam} 
	\state{Germany} 
	\postcode{14482}
}
\email{nils.strassenburg@student.hpi.de}

\begin{abstract}
Modern technologies enable people to share their opinions online at any time.
Thereby, the vast diversity of opinions requires a moderation of the discussions.
A prediction of the comment volume for unpublished articles could consequently help moderators to estimate the workload.
In contrast to existing work, we exclusively use deep learning to process article text and corresponding features to predict which articles will receive a large number of comments.
Hence, we achieve similar results as state-of-the-art approaches using traditional machine learning algorithms.
\end{abstract}

\begin{CCSXML}
	<ccs2012>
	<concept>
	<concept_id>10010147.10010178.10010179.10003352</concept_id>
	<concept_desc>Computing methodologies~Information extraction</concept_desc>
	<concept_significance>500</concept_significance>
	</concept>
	<concept>
	<concept_id>10010147.10010257.10010258.10010259.10010263</concept_id>
	<concept_desc>Computing methodologies~Supervised learning by classification</concept_desc>
	<concept_significance>500</concept_significance>
	</concept>
	<concept>
	<concept_id>10003456.10010927</concept_id>
	<concept_desc>Social and professional topics~User characteristics</concept_desc>
	<concept_significance>100</concept_significance>
	</concept>
	</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computing methodologies~Supervised learning by classification}
\ccsdesc[500]{Computing methodologies~Information extraction}
\ccsdesc[100]{Social and professional topics~User characteristics}

\keywords{Text mining}

\maketitle

\section{Introduction}
\input{introduction.tex}

\section{Dataset}
\input{dataset.tex}


\section{Methodology}
\input{methodology.tex}


\section{Evaluation}
\input{evaluation.tex}

\section{Conclusion}
\input{conclusion.tex}

\bibliographystyle{acm}
\bibliography{sigproc} 

\end{document}